---
title: "Schick_Lukas_Assignment5_R"
output: html_document
date: "2023-01-24"
---
https://github.com/slukas99/DSPM_Assignment5

```{r setup}
library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)

#get api key from seperate file
api_key <- source("API_key_A5.R")
```

## Exercises 1 - 6

Set up GitHub repository and get Ticketmaster API key, not no coding needed.

## Exercises 7 + 8

The resulting list gives information on the returned venues, a specific venue can be accessed by appending `_embedded`$venues[[x]] to the content object. In this way, information on a specific venue, like its name, address or city can be accessed. There is also additional information on the number of results per page, the number of pages, total results and the current page number and more. 

```{r}
#perform get request of ticketmaster site to get all venues in Germany
res <- GET(url = 'https://app.ticketmaster.com/discovery/v2/venues?', 
           query = list(apikey = api_key$value,
                        countryCode = 'DE'
                        ))
      

#extract content from response objects
ticketmaster <- content(res)

#initialize empty dataframe to store results
venues <- data.frame(matrix(0, ncol = 7, nrow = ticketmaster$page$size))
colnames(venues) <- c("name", "city", "postalCode", "address", "url", "longitude", "latitude")

#find out how many results are on the page
page_venues <- ticketmaster$`_embedded`$venues

#for each result on the page, do the following
for (i in 1:length(page_venues)){
  
  #get name, city, postalCode etc. if they are available, otherwise use NA
  if (is.null(page_venues[[i]]$name)){
    venues$name[i] <- NA
      } else {
        venues$name[i] <- page_venues[[i]]$name
        }
  if (is.null(page_venues[[i]]$city$name)){
    venues$city[i] <- NA
    } else {
      venues$city[i] <- page_venues[[i]]$city$name
      }
  if (is.null(page_venues[[i]]$postalCode)){
    venues$postalCode[i] <- NA
    } else {
      venues$postalCode[i] <- page_venues[[i]]$postalCode
      }
  if (is.null(page_venues[[i]]$address$line1)){
    venues$address[i] <- NA
    } else {
      venues$address[i] <- page_venues[[i]]$address$line1
      }
  if (is.null(page_venues[[i]]$url)){
    venues$url[i] <- NA
    } else {
      venues$url[i] <- page_venues[[i]]$url
      }
  if (is.null(page_venues[[i]]$location$longitude)){
    venues$longitude[i] <- NA
    } else {
      venues$longitude[i] <- page_venues[[i]]$location$longitude
      }
  if (is.null(page_venues[[i]]$location$latitude)){
    venues$latitude[i] <- NA
    } else {
      venues$latitude[i] <- page_venues[[i]]$location$latitude
    }
}

head(venues)

```

## Exercise 9

```{r}
#compute total number of result pages, count starts at 0, so take -1
num_pages <- ticketmaster$page$totalPages - 1

#initialize dataframe to store total results in
venues_total <- data.frame(name = NULL, city = NULL, postalCode = NULL, 
                           address = NULL, url = NULL, longitude = NULL, 
                           latitude = NULL)

#for each result page, do the following
for (j in 0:num_pages){
  
  #enforce pause in execution to adhere to rate limit (2 requests per second)
  Sys.sleep(.5)
  
  #perform get request of ticketmaster site to get all venues in Germany
  res <- GET(url = 'https://app.ticketmaster.com/discovery/v2/venues?', 
             query = list(apikey = api_key$value,
                          countryCode = 'DE',
                          page = j))
  
  #extract content from response objects
  ticketmaster <- content(res)
  
  #extract venue information into new object for easier access
  page_venues <- ticketmaster$`_embedded`$venues
  
  #check if there are results on the page (sometimes due to connection errors, no results will show up)
  if (length(page_venues) > 0) {
    
    #initialize empty dataframe to store results on this page
    venues <- data.frame(matrix(0, ncol = 7, nrow = length(page_venues)))
    colnames(venues) <- c("name", "city", "postalCode", "address", "url", "longitude", "latitude")
  
    #get name, city, postalCode etc. if they are available, otherwise use NA
    for (i in 1:length(page_venues)){
    
      if (is.null(page_venues[[i]]$name)){
        venues$name[i] <- NA
      } else {
        venues$name[i] <- page_venues[[i]]$name
      }
      if (is.null(page_venues[[i]]$city$name)){
        venues$city[i] <- NA
      } else {
        venues$city[i] <- page_venues[[i]]$city$name
      }
      if (is.null(page_venues[[i]]$postalCode)){
        venues$postalCode[i] <- NA
      } else {
        venues$postalCode[i] <- page_venues[[i]]$postalCode
      }
      if (is.null(page_venues[[i]]$address$line1)){
        venues$address[i] <- NA
      } else {
        venues$address[i] <- page_venues[[i]]$address$line1
      }
      if (is.null(page_venues[[i]]$url)){
        venues$url[i] <- NA
      } else {
        venues$url[i] <- page_venues[[i]]$url
      }
      if (is.null(page_venues[[i]]$location$longitude)){
        venues$longitude[i] <- NA
      } else {
        venues$longitude[i] <- page_venues[[i]]$location$longitude
      }
      if (is.null(page_venues[[i]]$location$latitude)){
        venues$latitude[i] <- NA
      } else {
        venues$latitude[i] <- page_venues[[i]]$location$latitude
      }
    }
    
    #append results of this page to total results
    venues_total <- rbind(venues_total,venues)
  }
  
}

```

```{r}
#print first ten results and shape of the total results dataframe
print(head(venues_total, 10))

print(dim(venues_total))
```

Note on the dimensions of venues_total: Because of a SpikeArrestViolation, the results of some pages are not available, even though the suggested pause of 0.2s between requests is included. This means that for any given run of the two code chunks above, the number of rows of the total results is not always the whole 4745, but may be up to 80 results less. (this means results for 4 pages are not included)

##Exercises 10 + 11

```{r}
#convert longitude and latitude to numeric for later use
venues_total$longitude <- as.numeric(venues_total$longitude)
venues_total$latitude <- as.numeric(venues_total$latitude)
```

```{r}
#remove venues with NAs for positional information
venues_total <- venues_total[!is.na(venues_total$longitude),]
```

```{r}
#get indices of results with "wrong" coordinates
false_coords <- as.numeric(venues_total$longitude) < 5.866 | as.numeric(venues_total$longitude) > 15.042 | 
  as.numeric(venues_total$latitude) < 47.270 | as.numeric(venues_total$latitude) > 55.059

```

```{r}
#remove results with "wrong" coordinates
venues_total <- venues_total[!false_coords,]

```

```{r}
#plot locations of results on a map of Germany
ggplot() +
  borders("world", "Germany", colour = "black", fill = "grey90") +
  geom_point(data = venues_total, aes(x = as.numeric(longitude), y = as.numeric(latitude))) + 
  theme_void() +
  coord_quickmap() +
  labs(title = "Event locations across Germany",
       caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic"))
```

##Exercise 12

```{r}
#perform get request of ticketmaster site to get all venues in France
res <- GET(url = 'https://app.ticketmaster.com/discovery/v2/venues?', 
           query = list(apikey = api_key$value,
                        countryCode = 'FR'
                        ))
      

#extract content from response objects
ticketmaster <- content(res)

#compute total number of result pages, count starts at 0, so take -1
num_pages <- ticketmaster$page$totalPages - 1

#initialize dataframe to store total results in
venues_total <- data.frame(name = NULL, city = NULL, postalCode = NULL, 
                           address = NULL, url = NULL, longitude = NULL, 
                           latitude = NULL)

#for each result page, do the following
for (j in 0:num_pages){
  
  #enforce pause in execution to adhere to rate limit (5 requests per second)
  Sys.sleep(.2)
  
  #perform get request of ticketmaster site to get all venues in France
  res <- GET(url = 'https://app.ticketmaster.com/discovery/v2/venues?', 
             query = list(apikey = api_key$value,
                          countryCode = 'FR',
                          page = j))
  
  #extract content from response objects
  ticketmaster <- content(res)
  
  #extract venue information into new object for easier access
  page_venues <- ticketmaster$`_embedded`$venues
  
  #check if there are results on the page (sometimes due to connection errors, no results will show up)
  if (length(page_venues) > 0) {
    
    #initialize empty dataframe to store results on this page
    venues <- data.frame(matrix(0, ncol = 7, nrow = length(page_venues)))
    colnames(venues) <- c("name", "city", "postalCode", "address", "url", "longitude", "latitude")
  
    #get name, city, postalCode etc. if they are available, otherwise use NA
    for (i in 1:length(page_venues)){
    
      if (is.null(page_venues[[i]]$name)){
        venues$name[i] <- NA
      } else {
        venues$name[i] <- page_venues[[i]]$name
      }
      if (is.null(page_venues[[i]]$city$name)){
        venues$city[i] <- NA
      } else {
        venues$city[i] <- page_venues[[i]]$city$name
      }
      if (is.null(page_venues[[i]]$postalCode)){
        venues$postalCode[i] <- NA
      } else {
        venues$postalCode[i] <- page_venues[[i]]$postalCode
      }
      if (is.null(page_venues[[i]]$address$line1)){
        venues$address[i] <- NA
      } else {
        venues$address[i] <- page_venues[[i]]$address$line1
      }
      if (is.null(page_venues[[i]]$url)){
        venues$url[i] <- NA
      } else {
        venues$url[i] <- page_venues[[i]]$url
      }
      if (is.null(page_venues[[i]]$location$longitude)){
        venues$longitude[i] <- NA
      } else {
        venues$longitude[i] <- page_venues[[i]]$location$longitude
      }
      if (is.null(page_venues[[i]]$location$latitude)){
        venues$latitude[i] <- NA
      } else {
        venues$latitude[i] <- page_venues[[i]]$location$latitude
      }
    }
    
    #append results of this page to total results
    venues_total <- rbind(venues_total,venues)
  }
  
}
```

```{r}
#print first ten results and shape of the total results dataframe
print(head(venues_total, 10))

print(dim(venues_total))
```

```{r}
#convert longitude and latitude to numeric for later use
venues_total$longitude <- as.numeric(venues_total$longitude)
venues_total$latitude <- as.numeric(venues_total$latitude)
```

```{r}
#remove venues with NAs for positional information
venues_total <- venues_total[!is.na(venues_total$longitude),]
```

```{r}
#get indices of results with "wrong" coordinates (only include mainland France)
false_coords <- as.numeric(venues_total$longitude) < -4.783 | as.numeric(venues_total$longitude) > 8.216 | 
  as.numeric(venues_total$latitude) < 42.333 | as.numeric(venues_total$latitude) > 51.083

```

```{r}
#remove results with "wrong" coordinates
venues_total <- venues_total[!false_coords,]

```

```{r}
#plot locations of results on a map of France
ggplot() +
  borders("world", "France", colour = "black", fill = "grey90") +
  geom_point(data = venues_total, aes(x = as.numeric(longitude), y = as.numeric(latitude))) + 
  theme_void() +
  coord_quickmap() +
  labs(title = "Event locations across France",
       caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic"))
```